Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-29 MDPI_submission.Rmd
Commit 2023-11-29 18:14

TSI$cor.null_value     <- NULL
TSI$cor.alternative    <- NULL
TSI$cor.method         <- NULL
TSI$cor.data_name      <- NULL
TSI$cor.p              <- NULL
care <- grep("^cor\\.", names(TSI), value = T )
for (an in care) {
    TSI[, (an) := NULL ]
}

>>>>

TSI$cor.null_value     <- NULL
TSI$cor.alternative    <- NULL
TSI$cor.method         <- NULL
TSI$cor.data_name      <- NULL
TSI$cor.p              <- NULL
TSI$conf.level         <- NULL
care <- grep("^cor\\.", names(TSI), value = T)
for (an in care) {
    TSI[, (an) := NULL ]
}
